\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliographie}

\bibitem{markowitz1952}
Harry Markowitz.
\textit{Portfolio Selection}.
The Journal of Finance, Vol. 7, No. 1, 1952, pp. 77-91.

\bibitem{markowitz1959}
Harry Markowitz.
\textit{Portfolio Selection: Efficient Diversification of Investments}.
John Wiley \& Sons, New York, 1959.

\bibitem{sharpe1964}
William F. Sharpe.
\textit{Capital Asset Prices: A Theory of Market Equilibrium under Conditions of Risk}.
The Journal of Finance, Vol. 19, No. 3, 1964, pp. 425-442.

\bibitem{sharpe1966}
William F. Sharpe.
\textit{Mutual Fund Performance}.
The Journal of Business, Vol. 39, No. 1, 1966, pp. 119-138.

\bibitem{lintner1965}
John Lintner.
\textit{The Valuation of Risk Assets and the Selection of Risky Investments in Stock Portfolios and Capital Budgets}.
The Review of Economics and Statistics, Vol. 47, No. 1, 1965, pp. 13-37.

\bibitem{fama1970}
Eugene F. Fama.
\textit{Efficient Capital Markets: A Review of Theory and Empirical Work}.
The Journal of Finance, Vol. 25, No. 2, 1970, pp. 383-417.

\bibitem{hochreiter1997}
Sepp Hochreiter and Jürgen Schmidhuber.
\textit{Long Short-Term Memory}.
Neural Computation, Vol. 9, No. 8, 1997, pp. 1735-1780.

\bibitem{lopez2018}
Marcos López de Prado.
\textit{Advances in Financial Machine Learning}.
John Wiley \& Sons, Hoboken, New Jersey, 2018.

\bibitem{lopez2020}
Marcos López de Prado.
\textit{Machine Learning for Asset Managers}.
Cambridge University Press, Cambridge, 2020.

\bibitem{black1992}
Fischer Black and Robert Litterman.
\textit{Global Portfolio Optimization}.
Financial Analysts Journal, Vol. 48, No. 5, 1992, pp. 28-43.

\bibitem{bengio1994}
Yoshua Bengio, Patrice Simard, and Paolo Frasconi.
\textit{Learning Long-Term Dependencies with Gradient Descent is Difficult}.
IEEE Transactions on Neural Networks, Vol. 5, No. 2, 1994, pp. 157-166.

\bibitem{fischer2018}
Thomas Fischer and Christopher Krauss.
\textit{Deep learning with long short-term memory networks for financial market predictions}.
European Journal of Operational Research, Vol. 270, No. 2, 2018, pp. 654-669.

\bibitem{goodfellow2016}
Ian Goodfellow, Yoshua Bengio, and Aaron Courville.
\textit{Deep Learning}.
MIT Press, Cambridge, Massachusetts, 2016.

\bibitem{hull2021}
John C. Hull.
\textit{Machine Learning in Business: An Introduction to the World of Data Science (3rd Edition)}.
Amazon KDP, 2021.

\bibitem{malkiel1973}
Burton G. Malkiel.
\textit{A Random Walk Down Wall Street}.
W. W. Norton \& Company, New York, 1973.

\bibitem{kahneman1979}
Daniel Kahneman and Amos Tversky.
\textit{Prospect Theory: An Analysis of Decision under Risk}.
Econometrica, Vol. 47, No. 2, 1979, pp. 263-291.

\bibitem{taleb2007}
Nassim Nicholas Taleb.
\textit{The Black Swan: The Impact of the Highly Improbable}.
Random House, New York, 2007.

\bibitem{gu2020}
Shihao Gu, Bryan Kelly, and Dacheng Xiu.
\textit{Empirical Asset Pricing via Machine Learning}.
The Review of Financial Studies, Vol. 33, No. 5, 2020, pp. 2223-2273.

\bibitem{dixon2020}
Matthew F. Dixon, Igor Halperin, and Paul Bilokon.
\textit{Machine Learning in Finance: From Theory to Practice}.
Springer, Cham, Switzerland, 2020.

\bibitem{chollet2017}
François Chollet.
\textit{Deep Learning with Python}.
Manning Publications, Shelter Island, New York, 2017.

\bibitem{yfinance2024}
Yahoo! Finance API.
\textit{yfinance Library Documentation}.
\url{https://github.com/ranaroussi/yfinance}, consulté en 2024.

\bibitem{pyportopt2024}
Robert Andrew Martin.
\textit{PyPortfolioOpt: Portfolio Optimization in Python}.
Journal of Open Source Software, Vol. 6, No. 61, 2021, p. 3066.

\end{thebibliography}
